The Hot Hand in Call of Duty Search and Destroy

### 2022-08-21 paper/paper.Rmd
p7 feedback

@@

[^21]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.

```{=tex}
\begin{longtable}{rcrrrrr}
\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r}$, and proportion of round wins, $P^{+|k,r}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r} = \frac{r^{+|k,r}}{N^{kr}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively.}
\label{tbl:cod-pw3r-pl3r} \\

\toprule
$r$ & \text{Win series?} & $r^{+|k,r}$ & $N^{kr}$ & $P^{+|k,r}$ & $\hat{P}^{+|k,r}_0$ & $\hat{P}^{+|k,r}_{MS}$ \\ 
\midrule

@@

```{=tex}
\begin{longtable}{rrcrrrr}
\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r,i}$, and proportion of round wins, $P^{+|k,r,i}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r,i} = \frac{r^{+|k,r,i}}{N^{kri}}$). Additionally, the notional proportion, $\hat{P}^{+|k,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k,r,i}_0$ to the observed proportion $P^{+|k,r,i}$. Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
\label{tbl:cod-pw3ri-pl3ri} \\
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k,r,i}$ & $N^{kri}$ & $P^{+|k,r,i}$ & $\hat{P}^{+|k,r,i}_0$\\ 
\midrule

@@

For the sake of brevity, We did not delve into win rates and streaks split by offensive or defensive role. For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team. This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average. On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx$ 13.0%---so We would want to account for sample size differences.

@@

# Acknowledgements {.unnumbered}

Thank our brother Andrew for giving me feedback on drafts of this paper.

>>>>

### Post-streak probability

@@

[^21]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.

```{=tex}
\begin{longtable}{rcrrrrr}
\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
\label{tbl:cod-pw3r-pl3r} \\

\toprule
$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=3k,r}_{MS}$ \\ 
\midrule

@@

```{=tex}
\begin{longtable}{rrcrrrr}
\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak ($P^{+|k=3,r,i} = \frac{r^{+|k=3,r,i}}{N^{k=3,r,i}}$). Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k=3,r,i}_0$ to the observed proportion $P^{+|k=3,r,i}$. Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{k=3,r,i} \geq 10$ for brevity.}
\label{tbl:cod-pw3ri-pl3ri} \\
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
\midrule

@@

For the sake of brevity, we did not delve into win rates and streaks split by offensive or defensive role. For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team. This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average. On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx$ 13.0%---so We would want to account for sample size differences.

@@

Other talking points

-   We probably should have expected no hot hand effect given the small "skill gap" in the CoD relative to other esports (andecdotal, but most professional esports player, including CoD players themselves, would say this).

### 2022-08-21 paper/paper.tex
p7 feedback

Given that people typically perceive streaks as beginning after the
third success (or failure) at minimum (Carlson and Shu 2007), We focus
on streaks of three round wins.\footnote{Three happens to also be a
  reasonable number for series that lasts at maximum 11 rounds.} Table
\ref{tbl:cod-pw3r-pl3r} compares the observed round win rate
\(P^{w,kr}\) following streaks of \(k=3\) round wins given the series
outcome (\(r\) rounds and winner) with the notional and MS expected
proportions, \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\)
respectively.

\begin{longtable}{rcrrrrr}
\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r}$, and proportion of round wins, $P^{+|k,r}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r} = \frac{r^{+|k,r}}{N^{kr}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively.}
\label{tbl:cod-pw3r-pl3r} \\

\toprule
$r$ & \text{Win series?} & $r^{+|k,r}$ & $N^{kr}$ & $P^{+|k,r}$ & $\hat{P}^{+|k,r}_0$ & $\hat{P}^{+|k,r}_{MS}$ \\ 
\midrule

@@

\begin{longtable}{rrcrrrr}
\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r,i}$, and proportion of round wins, $P^{+|k,r,i}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r,i} = \frac{r^{+|k,r,i}}{N^{kri}}$). Additionally, the notional proportion, $\hat{P}^{+|k,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k,r,i}_0$ to the observed proportion $P^{+|k,r,i}$. Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
\label{tbl:cod-pw3ri-pl3ri} \\
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k,r,i}$ & $N^{kri}$ & $P^{+|k,r,i}$ & $\hat{P}^{+|k,r,i}_0$\\ 
\midrule

@@

@@

For the sake of brevity, We did not delve into win rates and streaks
split by offensive or defensive role. For example, it would be
interesting to look at whether the round win rate is higher after a
streaks of three round wins when the team starts the streak winning as
the offensive team. This would mean that, in the round immediately
following the streak, the streaking team would be playing defense, where
teams are slightly more likely to win on average. On the other hand,
streaks of three starting with an offensive round win---theoretically,
given \(\tau_O\) = 47.7\% the expected frequency is
\(\tau_O^2 \times (1 - \tau_O) \approx\) 11.9\%---are likely to occur
less frequently than such streaks starting with a defensive
win---\(\tau_O \times (1 - \tau_O)^2 \approx\) 13.0\%---so We would want
to account for sample size differences.

@@

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

Thank our brother Andrew for giving me feedback on drafts of this paper.

>>>>

\hypertarget{post-streak-probability}{%
\subsubsection{Post-streak probability}\label{post-streak-probability}}

Given that people typically perceive streaks as beginning after the
third success (or failure) at minimum (Carlson and Shu 2007), We focus
on streaks of three round wins.\footnote{Three happens to also be a
  reasonable number for series that last at maximum 11 rounds.} Table
\ref{tbl:cod-pw3r-pl3r} compares the observed round win rate
\(P^{w,kr}\) following streaks of \(k=3\) round wins given the series
outcome (\(r\) rounds and winner) with the notional and MS expected
proportions, \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\)
respectively.

\begin{longtable}{rcrrrrr}
\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
\label{tbl:cod-pw3r-pl3r} \\

\toprule
$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=3k,r}_{MS}$ \\ 
\midrule

@@

\begin{longtable}{rrcrrrr}
\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak ($P^{+|k=3,r,i} = \frac{r^{+|k=3,r,i}}{N^{k=3,r,i}}$). Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k=3,r,i}_0$ to the observed proportion $P^{+|k=3,r,i}$. Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{k=3,r,i} \geq 10$ for brevity.}
\label{tbl:cod-pw3ri-pl3ri} \\
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
\midrule

@@

\hypertarget{wald-wolfowitz-runs-test-1}{%
\subsubsection{Wald-Wolfowitz runs
test}\label{wald-wolfowitz-runs-test-1}}

@@

For the sake of brevity, we did not delve into win rates and streaks
split by offensive or defensive role. For example, it would be
interesting to look at whether the round win rate is higher after a
streaks of three round wins when the team starts the streak winning as
the offensive team. This would mean that, in the round immediately
following the streak, the streaking team would be playing defense, where
teams are slightly more likely to win on average. On the other hand,
streaks of three starting with an offensive round win---theoretically,
given \(\tau_O\) = 47.7\% the expected frequency is
\(\tau_O^2 \times (1 - \tau_O) \approx\) 11.9\%---are likely to occur
less frequently than such streaks starting with a defensive
win---\(\tau_O \times (1 - \tau_O)^2 \approx\) 13.0\%---so We would want
to account for sample size differences.

@@

Other talking points

\begin{itemize}
\tightlist
\item
  We probably should have expected no hot hand effect given the small
  ``skill gap'' in the CoD relative to other esports (andecdotal, but
  most professional esports player, including CoD players themselves,
  would say this).
\end{itemize}
